### 2021-01-30 Phys 311/CTA Paper/main.tex
Move folder

	\textsc{\Large CTA Term Paper}\\[0.5cm] % Major heading such as project name

@@

	%------------------------------------------------
	%	Logo
	%------------------------------------------------

	%\vfill\vfill
	%\includegraphics[width=0.2\textwidth]{placeholder.jpg}\\[1cm] % Include a department/university logo - this will require the graphicx package

@@

\section{Description}
This is a test Hiring Professionals (KajLagbe) is a platform for publishing and finding jobs that are not so conventional to the existing job marketplace. We focus on providing manpower specially for the day to day requirements.
\newline 
\newline
So, there are specially two types of user that will use this platform. One of them will be the Professionals with actual skills and the other type of the user will be the Consumer who will consume the service.
\newline
\newline
Consumers can post jobs specifying the skill that is needed for the job.
Professionals can provide their skills during registration, which will be the key to finding all of the available jobs. Professionals can also search jobs based on location.
\newline
\newline
When professionls see a job post s/he can comment on the post to seek the attention of the consumer. Then comment is posted successfully s/he will be regarded as an interested user and option will be available to consumer to submit contract to the professional. Multiple professionals can be interested. Consumer can choose among them based on their rating / skill / daily charge.
\newline
\newline
When contract is submitted to a professional, the contract will be visible to the contracts page of the professional. If a professional accepts the contract the job will be restricted for all other users to accept.
\newline
\newline
When a professional completes a job he will have to press Job Completed button which will generate the receipt with the bill. Professionals can then rate the consumer or return to home page. In the same way consumers will also get an option to rate the professional who has completed his job.

@@

Applications of our project is as follows:
\begin{itemize}
\item \textbf{Application 1: } Find jobs based on skills and place.
\item \textbf{Application 2: } Get suggestions of daily jobs that match your skills.
\item \textbf{Application 3: } Get the list of all of your contracts that are currently in place.
\item \textbf{Application 4: } Keep track of your completed jobs along with the earnings.
\item \textbf{Application 5: } Posting jobs that requires a specific skill
\item \textbf{Application 6: } Get the list of top employers
\item \textbf{Application 7: } Generate receipt based on the time duration of a service
\item \textbf{Application 8: } Comment on posts published by consumers
\item \textbf{Application 9: } Rating enabled for consumers and professionals when job is finished
\item \textbf{Application 10: } Each user have their own profile with all of their basic information, professionals have their skills also

\end{itemize}

>>>>

	\textsc{\Large CTA Proposal}\\[0.5cm] % Major heading such as project name

@@

@@

\section{Topic Background}

@@
